Some Nice Title Goes Here, Eventually\ldots

### 2014-08-25 doc/tacs2014/article.tex
Elaborated slightly on previous work, experiments, and future work. Added overview diagram and bibtex.

\documentclass[10pt,conference,a4paper]{IEEEtran}
\usepackage{hyperref}
%\usepackage{

@@

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \texttt{fredrik.karlstrm@uabc.edu.mx}}
	\and
	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \texttt{your-cool-academic-email-here@uabc.edu.mx}}
}

@@

	\begin{abstract}
		Oh golly, this is where the abstract should go.
		``I can hardly wait to begin writing it!''

		Or well, let's see how things turn out in the body first, eh.
	\end{abstract}
	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, Japanese writing, \ldots
	\end{IEEEkeywords}

@@

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list [ref] defines a set of 2,136
	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive though:
	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji characters.

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, depending on
	deep neural networks [ref?] for high performance.

@@

	Thus concludes this tale of Foo Bar, whose epic journey had a tremendous
	impact on the field of cryptography. Thank you, Foo, for your contributions.

@@

	%\begin{figure}
	%\centering
	%\includegraphics[width=2.5in]{myfigure}
	%\caption{Simulation Results}
	%\label{fig_sim}
	%\end{figure}

	\subsection{Stroke feature extraction}

@@

@@

	\section{References}

>>>>

\documentclass[10pt,conference,a4paper]{IEEEtran}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
%\usepackage{

@@

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:fredrik.karlstrm@uabc.edu.mx}{\texttt{fredrik.karlstrm@uabc.edu.mx}}}
	\and
	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:foo@bar.com}{\texttt{your-cool-academic-email-here@uabc.edu.mx}}}
}

@@

	\begin{abstract}
		Quick content summary.
		Motivation. (From 'Robust': High accuracy has been attained, but speedup/size improvements still important for mobile and desktop.)
	\end{abstract}
	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, Japanese writing, \ldots
	\end{IEEEkeywords}

@@

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive, though:
	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, requiring
	deep neural networks \cite{ciresan2012multi} to attain high recognition rates.

@@

	Testing a cite \cite{zhu2014robust}.

	\ldots

	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
	hidden Markov models for the purpose of online kanji recognition. By identifying and classifying
	substrokes, which in turn are employed as search keys in a character dictionary, this approach vastly
	reduced the memory requirements for both their models and their dictionary.

	``Online Handwritten Kanji Recognition Based on Inter-stroke Grammar'' uses the A-H0-9 classification scheme,
	and discusses the hierarchical structure of kanji.

	Should we mention alternative solutions, such as SVMs?

@@

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/model-overview.eps}
		\caption{Model overview. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
		\label{fig_model_overview}
	\end{figure}

	\subsection{Feature extraction}

@@

	\ldots

	Whereas in \cite{nakai2001substroke} strokes were segmented into substrokes and classified in
	25 dimensions, our initial feature extraction strategy provides a coarse full--stroke classification
	in 8 dimensions. By discarding ``pen--up motions,'' we render the system more resilient to erroneous
	stroke order, at the cost of increasing variability within each cluster.

@@

	\section{Future work}

	The experimental results documented in this paper are an initial attempt at applying the proposed methodology;
	numerous variations remain to be explored. With regard to online recognition, the explored feature extraction
	strategy could be enhanced to break strokes into substrokes, diffentiate between long and short strokes, and take
	pen--up movements into account. This alteration would in turn allow clustering on up to 25 dimensions, rather than the current 8.

	By substituting the current coarse classifier with an offline feature extraction strategy, the entire system could
	be evaluated on offline handwriting recognition datasets, such as\ldots.

	Clustering\ldots

	Finally, at the cluster--specific CANN--level, there is ample opportunity to tweak the network topology as well as
	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine--grain recognition results.

	%\section{References}
	\bibliography{./references}
